IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/intro.tex
typo

In the alternative \textit{coarse-grained} approach to IFC,
a system is divided into relatively course computational units,
each with a single label dictating its security policy.
Only
communication between isolated computational units must be tracked.
A recent system named SWAPI adds IFC to the
browser by identifying \emph{Web workers} as an existing computational
unit~\cite{swapi}.  Communication between workers is mediated using
IFC to ensure non-interference, preventing sensitive workers from
influencing the computation of less sensitive workers.
This coarse-grained approach provides a number of advantages:
(1) reduced runtime overhead because checks need only
be performed at isolation boundaries, (2) minimal changes to an
existing programming language when adding IFC, which (3) allows
the reuse of existing programs.  Finally, (4) associating
a single security label with the entire computational unit simplifies
understanding and easy reasoning about the correctness of the
system, without information-flow reasoning about the
technical details of the semantics of the programming language.

@@

One challenge in the design of our system is that the semantics for the
retrofitted IFC language may not accurately correspond to the optimized
implementation details of a particular target language.
We discuss and partially address this issue
by characterizing isomorphisms between the operational semantics of our
defined language and a concrete implementation, showing that if this
relationship holds, then noninterference in the abstract specification
carries over to the concrete specification.

>>>>

In the alternative \textit{coarse-grained} approach to IFC,
a system is divided into relatively coarse computational units,
each with a single label dictating its security policy.
Only
communication between isolated computational units must be tracked.
A recent system named SWAPI adds IFC to the
browser by identifying \emph{web workers} as an existing computational
unit~\cite{swapi}.  Communication between workers is mediated using
IFC to ensure non-interference, preventing sensitive workers from
influencing the computation of less sensitive workers.
This coarse-grained approach provides a number of advantages:
(1) reduced runtime overhead because checks need only
be performed at isolation boundaries, (2) minimal changes to an
existing programming language when adding IFC, which (3) allows
the reuse of existing programs.  Finally, (4) associating
a single security label with the entire computational unit simplifies
understanding and reasoning about the correctness of the
system, without information flow reasoning about the
technical details of the semantics of the programming language.

@@

One challenge in the design of our system is that the semantics for the
retrofitted IFC language may not accurately correspond to the optimized
implementation details of a particular target language.
We discuss and partially address this issue
by characterizing isomorphisms between the operational semantics of our
defined language and a concrete implementation, showing that if this
relationship holds, then non-interference in the abstract specification
carries over to the concrete specification.
